Classless Java

### 2015-11-10 paper/sections/RelatedWork.tex
Text reorganization

\subsection{Formalization of Java8}
\marco{this go later, when we compare our formalization}
There is also formalization proposed by
Goetz and Field~\cite{goetz12fdefenders} to formalize defender (default) methods
in Java. However this formalization is limited since they only model exactly one
method inside classes/interfaces, where in our formalization multiple methods
may be defined.

@@

>>>>

@@

\subsection{Formalization of Java8}
We provide a simple and well designed formalization for a subset of Java including default/static interface methods and object initialization literals (often called anonymous local inner classes).
A similar formalization was drafted by\marco{ I use the term draft because I seams to remember it was just a technical report, I'm right?}
Goetz and Field~\cite{goetz12fdefenders} to formalize defender (default) methods
in Java. However this formalization is limited to model exactly one
method inside classes/interfaces.

As a evidence of the attention and care present in our formalization work, while double-checking the behaviour of Java in side cases we have discovered a likely bug in the current \texttt{javac}.\marco{refer to before when we explain the issue.}
